Dynein notes

### 2018-02-13 papers/notes/notes.tex
turned reorganize into root
add a small notes

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{figures/equilibrium-onebound}
  \caption{Definition of equilibrium angles.}
  \label{fig:eq_angles}
\end{figure}

@@

\section{Papers}
\subsection{Native dynein cryo-EM structure}
Full structure of dynein.\\

@@

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{../elliott-thesis/figures/equilibrium-onebound}
  \caption{Definition of equilibrium angles.}
  \label{fig:eq_angles}
\end{figure}

@@

\section{Papers}
\subsection{Native dynein cryo-EM structure}
Structural organization of the dynein-dynactin complex bound to microtubules\\

Full structure of dynein.\\

@@

to discuss:
        gibbs-bd transitions look much better
        hard to run simulations with the current nan-unbinding code - is there a better way? could we just sample from a positive gaussian instead?
        yildiz-inspired transition model: at low separation atpase unbinding rate; at high internhead, feel 1pN force per 12nm
                        Could use the release rate modifiers from the Yildiz rate vs separation plots
